### 2014-05-21 intro.tex
More intro tweaks

Despite its demonstrable success, this approach can have downsides. In
defining transport-layer protocols by their \emph{mechanisms}---by the
actual behavior of endpoints or gateways that execute the
protocol---we leave implicit the assumptions that the mechanism makes
about the behavior of other layers and the policy that the mechanism
is built to pursue.

For contemporary mechanisms (e.g., TCP Cubic, the current default in
Linux), it's difficult to state the assumptions that the transport
makes about lower layers and to predict when those assumptions would
no longer hold. This presents a challenge for link-layer designers who
wish to design a new networking technology. Because of Cubic's
popularity, it has become a \emph{de facto} requirement that Cubic perform
well over any new network. In effect, this means that the designer of
the new link layer must try to satisfy Cubic's implicit assumptions in
order to achieve adequate performance.

This has led to the ``bufferbloat''\cite{bufferbloat} problem:
believing that the transport layer will interpret losses as a
signal to slow down, the link layer tries to drop packets as
rarely as possible. It has also led to a lack of parallelism in
Internet routing---flows only take one path, even if speedups might be
available by splitting flows across multiple routes---on the grounds
that the transport protocol might interpret out-of-order packets
as a pathology.

On the flip side, it is usually impossible to adjust the transport
layer's assumptions in order to accommodate a new kind of
link. There's no way to tweak the assumptions and then retrace the
same design process that the protocol's designers followed, to find the
mechanism they would have produced given a different starting point.

%\section{Showing our work in protocol design}

This thesis proposes essentially that approach to protocol design. The
transport layer should adapt to whatever the layers below may do, and
whatever the application above it wants done. Protocol designers
should specify the \emph{policy}---namely, what assumptions they want
to make about the network and what kind of performance the application
is interested in---and let computers worry about translating that into
the mechanism of congestion control.

By ``showing our work'' in this way, clearly enough for a computer to
recreate the same design, altering the assumptions is a matter of
changing the inputs to a computer program. This makes it easier for
adjacent layers to evolve. My colleagues and I have also found that
this approach can yield better performance than conventional,
human-designed protocols.

>>>>

Despite its success, this approach imposes costs. In defining
transport-layer protocols by their \emph{mechanisms}---by the actual
behavior of endpoints that execute the protocol---we leave implicit
the assumptions that the mechanism makes about the behavior of other
layers and the policy that the mechanism is built to pursue.

For contemporary protocols (e.g., TCP Cubic, the current default in
Linux), it's challenging to state the assumptions that the transport
makes about lower layers and to predict when those assumptions will no
longer hold. This presents a difficulty for link-layer designers who
wish to create new networking technologies. Because of Cubic's
prevalence, it has become a \emph{de facto} requirement that Cubic
perform well over any network. To achieve adequate performance, the
designer of the new link layer must make sure to satisfy Cubic's
implicit assumptions.

This has led to the ``bufferbloat''\cite{bufferbloat} problem:
believing that the transport layer will interpret losses as a signal
to slow down, the network tries to drop packets as rarely as
possible. It has also led to a lack of parallelism in Internet
routing---flows only take one path, even if striping across
multiple paths could yield a speedup---on the grounds that the
transport protocol might interpret out-of-order packets as a
pathology.

On the flip side, it is not easy to adjust the transport
layer's assumptions in order to accommodate a new kind of
network. There's no way to tweak the requirements and then retrace the
same design process that the protocol's designers followed, to find the
mechanism they would have produced given a different starting point.

\section{Showing our work in protocol design}

This thesis proposes that the transport layer should adapt
programmatically to whatever the layers below may do, and whatever the
application above it wants. Protocol designers should specify the
\emph{policy}---namely, what assumptions they want to make about the
network and what kind of performance the application is interested
in---and let computers worry about translating this into the mechanism
of congestion control.

By ``showing our work'' in this way, clearly enough for a computer to
recreate the same design, tweaking the assumptions is a matter of
changing the inputs to a computer program and running it again. My
colleagues and I have found that this approach yields better
peformance than conventional protocols, while allowing adjacent layers
to evolve more freely.
